\begin{comment}
\item Guest
\begin{enumerate}
  \item Registration
  \begin{itemize}
  \item She has to provide her credentials. 
  \item She has to provide her payment information.
  \item The system shall give back a password that can be used for log-in.

  \end{itemize}
  \item Log-in
  \begin{itemize}
  \item She has to provide her \gls{ID}.
  \item She has to provide her \gls{pwd}.
  %\item 

  \end{itemize}
  
  \end{enumerate}
\item User
\begin{enumerate}
  
  \item Find a car
  \begin{itemize}
  \item The system shall provide the location af all the avaible cars around the selected area.
  \item The system may know the user's location. Not necessary but useful.
  \item The system shall implement a map of the world considered.
  \end{itemize}
  
  \item Reserve a car
  \begin{itemize}
  \item The system shall kwon if a car is avaible or not.
  \item The system shall know if an user is already reserving a car.
  \item The system shall turn a car avaible or not avaible.x
  \item The system shall know the time when an user do a reservation.
  \item The system shall tag a car avaible again if a car is not picked-up within an hour from the reservation.
  \end{itemize}
  
  \item Unlock a car
  \begin{itemize}
  \item The system shall unlock a car when an user, who reaches a reserved car, tells to the system that she is nearby.
  \end{itemize}


  \item Use a car
  \begin{itemize}
  \item The system shall let each user to use only a single car at a time.
  \item The system shall start to calculate the charge as soon as the engine ignites.
  \item The system shall calculate the current cherges. The amount of money per minute is gived.
  \item The system shall notified the current charges to the user through a screen on the car.
  \end{itemize}
  
  \item Pyment
  \begin{itemize}
  \item The system shall charge the user using her payment information after each utilization.
  \item The system shall start to calculate the charge as soon as the engine ignites.
  \item The system shall stop to calculate the charge as soon as the car is parked in a safe area and the user exits the car.%same moment that the car is locked
  \item The system should apply a discount of 10\% on the last ride if it detects the user took at least two other passengers onto the car.
  \item The system should apply a discount of 20\% on the last ride if the car is left with no more than 50\% of the battery empty.
  \item The system should apply a discount of 30\% on the last ride If the car is left at special parking areas where they can be recharged and the user takes care of plugging the car into the power grid.
  \item The system should charge 30\% more n the last ride if a car is left at more then 3 KM  from the nearest power grid station or with more than 80\% of the battery empty.
  \item The system shall apply a fee of 1 EUR if a car is not picked-up within an hour from the reservation.
  \end{itemize}

  \item Lock a car
  \begin{itemize}
  \item The system shall lock the car when an user has parked the car in a safe area and the user exits the car. 
  \end{itemize}

\end{enumerate}
\end{comment}


Looking at the objectives and success criteria of the project described in section 1.3, we can derive the functional requirements that PowerEnJoy have to implement. We choosed to group them by the actor involved in the function.
\begin{itemize}
  \item Guest
  \begin{enumerate}
    \item Registration
    \item Log-in
  \end{enumerate}
  \item User
  \begin{enumerate}
    \item Find a car
    \item Reserve a car
    \item Unlock a car
    \item Use a car
    \item Payment
    \item Lock a car
  \end{enumerate}
\end{itemize}

% maybe classification table (http://www.pages.drexel.edu/~sga72/docs/SRSwithUseCases.pdf)
\begin{center}
  \vspace{0.6cm}
  \begin{tabular}{|l|l|l|l|}
      \hline
      Use-case & Actor & Brief description & Goal \\\hline
      \hline
      1 & Guest & Registration & G\ref{itm:goal-registration} \\\hline
      2 & Guest & Log-in & G\ref{itm:goal-access} \\\hline
      3 & User & Reservation & G\ref{itm:goal-reservation} \\\hline
      4 & User & Use & G\ref{itm:goal-locking} \\\hline
      5 & User & Payment & G\ref{itm:goal-payment} \\\hline
  \end{tabular}
\end{center}
\begin{comment}
  \newpage
  \subsection{Sample section}
  This section is here just to provide a standard template for the system functions, before the functional requirements enumeration a brief description may be useful
  \subsubsection{Functional requirements}
  \subsubsection{Scenario 1}
  \subsubsection{Scenario 2}
  \subsubsection{Scenario n}
  \subsubsection{Use-case table}
  \subsubsection{Use-case diagram}
  \subsubsection{Activity/State-chart diagram}
  \subsubsection{Sequence diagram}
  \subsubsection{Mockups}
\end{comment}

\newpage
\subsection{Registration}
  \input{contents/Requirements_Specification/System_Functions/Registration}

\newpage
\subsection{Log-in}
  \input{contents/Requirements_Specification/System_Functions/Login}

\newpage
\subsection{Create Reservation}
  \input{contents/Requirements_Specification/System_Functions/Create_Reservation}
  
\newpage

\subsection{Menage account}
  \input{contents/Requirements_Specification/System_Functions/Menage_account}
  
\newpage
\subsection{Delete Reservation}
  \input{contents/Requirements_Specification/System_Functions/Delete_Reservation}

